implementation quality control

### 2018-03-27 analysis/analyses/4-method_characterisation/7_quality_control.Rmd
cleanup method characterisation

g2 <- ggplot(implementations_evaluated %>% mutate(Citations = ifelse(Citations == 0, 0.5, Citations)), aes(date, Citations)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_text_repel(aes(label = label_implementation(implementation_id))) +
    scale_y_log10() +
    labs(x = "Time", y = "Citations", title = "Citations over time")
g2

g3 <- ggplot(implementations_evaluated %>% mutate(Citations = ifelse(Citations == 0, 0.5, Citations)), aes(Citations, qc_score)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_text_repel(aes(label = label_implementation(implementation_id))) +
    scale_x_log10() +
    labs(x = "Citations", y = "QC score", title = "QC score over # citations")
g3

>>>>

g2 <- ggplot(implementations_evaluated %>% mutate(ncitations = ifelse(ncitations == 0, 0.5, ncitations)), aes(date, ncitations)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_text_repel(aes(label = label_implementation(implementation_id))) +
    scale_y_log10() +
    labs(x = "Time", y = "Citations", title = "Citations over time")
g2

g3 <- ggplot(implementations_evaluated %>% mutate(ncitations = ifelse(ncitations == 0, 0.5, ncitations)), aes(ncitations, qc_score)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_text_repel(aes(label = label_implementation(implementation_id))) +
    scale_x_log10() +
    labs(x = "Citations", y = "QC score", title = "QC score over # citations")
g3
